Gamification Effectiveness on Education

### 2024-04-18 paper/paper.qmd
Finish limatations and weakness section

# Data

## Data Source

This paper reproduces the result from called "On the effectiveness of game-like and social approaches in learning: Comparing educational gaming, gamification & social networking" (@DEMARCOS2017155). This paper will provided a overview of the data used in that study. For more detailed explanation of the data please visit the original study.

## Methodology

The original study used 379 undergraduates for their experiments and there were randomly assigned into 5 groups Control(N=76), Educational game(N=75), Gamification Plugin(N=77), Social networking website(N=75), Social gamified networking website(N=76). The experiment was carried out on 10-week first year undergraduate class called ‘Qualification for ICT Users’ with blended learning. This course is an introduction to basic computing concepts such as word processing, spreadsheets, presentations and databases.

@@

## Variables of Interest and Data Cleaning Procedure
The variables used in this study are Group, Gender, pretest and post test for Word Processing, Spreadsheets, Presentation, Databases and FinalExamination. Pretest, post test and FinalExamination use the measurement of a grade, which is from 0 - 100%.

@@

# Results

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: tbl-pretest
#| tbl-cap: "The results of the pretest."

@@

Another example that we want to apply this framework is on a popular gamification language learning app, called Duolingo. Duolingo is a free app that has miliions of user ranging from public students in third world countries to even hollywood stars. Yu-kai Chou website provides an analysis for Duolingo, which has 6 out of 8 elements of the framework and here I am going to highlight some of the elements. Firstly, Epic Meaning is to learn a language and the app even asks the user when creating an account what is their purpose for learning new language. Secondly, Ownership, users have a currency call Lingots which allows players to buy Power-Ups(ways to make the player stronger) such as streak freeze and to buy clothes for their player character. Lastly, it has Scarcity and Avoidance as player have a limited amount of lives and if they lose then they can no longer play for a certain of time. 
## Student's feedback

## Weaknesses and next steps

>>>>

# Data
## Data Source
This paper reproduces the result from called "On the effectiveness of game-like and social approaches in learning: Comparing educational gaming, gamification & social networking" (@DEMARCOS2017155). This paper will provided a overview of the data used in that study. For more detailed explanation of the data please visit the original study.

## Methodology
The original study used 379 undergraduates for their experiments and there were randomly assigned into 5 groups Control(N=76), Educational game(N=75), Gamification Plugin(N=77), Social networking website(N=75), Social gamified networking website(N=76). The experiment was carried out on 10-week first year undergraduate class called ‘Qualification for ICT Users’ with blended learning. This course is an introduction to basic computing concepts such as word processing, spreadsheets, presentations and databases.

@@

## Variables of Interest and Data Cleaning Procedure

The variables used in this study are Group, Gender, pretest and post test for Word Processing, Spreadsheets, Presentation, Databases and FinalExamination. Pretest, post test and FinalExamination use the measurement of a grade, which is from 0 - 100%.

@@

# Results
```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: tbl-pretest
#| tbl-cap: "The results of the pretest."

@@

Another example that we want to apply this framework is on a popular gamification language learning app, called Duolingo. Duolingo is a free app that has miliions of user ranging from public students in third world countries to even hollywood stars. Yu-kai Chou website provides an analysis for Duolingo, which has 6 out of 8 elements of the framework and here I am going to highlight some of the elements. Firstly, Epic Meaning is to learn a language and the app even asks the user when creating an account what is their purpose for learning new language. Secondly, Ownership, users have a currency call Lingots which allows players to buy Power-Ups(ways to make the player stronger) such as streak freeze and to buy clothes for their player character. Lastly, it has Scarcity and Avoidance as player have a limited amount of lives and if they lose then they can no longer play for a certain of time.

## Limations and Weaknessess
Limitations of this dataset is that doesn't tell us how student's satisfaction, retention, motivation and engagement. This is would useful information since it will paint us better picture on the effectiveness of gamification. In addition, if students don't really like then it would be indicator whether gamification is not working or that something missing that could improve it. According to (@article), some aspects of academic boredom comes from lack of motivation and learning methods, so if gamification can solve this would a huge win for students and for society at a whole. Furthermore, if students really enjoy gamification then this means this a potential valid leanring method, which could convince others to fund and study further.

Weakness of this dataset is that age column take the average age, which is 19 years in this case and gives every student that age. If the dataset gave us every student's age or even age range this could useful in determining which age group was benefiting more from gamification. It could that told us younger students better with gamification, but old students preform better with the traditional learning system.

## Future Studies
